The globular cluster system of the Auriga simulations

### 2019-10-28 AurigaGCS.tex
Process feedback referee / General comments about style / acronyms need to be introduced

% Abstract of the paper
\begin{abstract}
We investigate whether the galaxy and star formation model used for the Auriga
simulations can produce a realistic GC population. We compare statistics of GC 
candidate star particles in the Auriga haloes with catalogues of the Milky Way 
(MW) and Andromeda (M31) GC populations. We find that the Auriga simulations do 
produce sufficient stellar mass for GC candidates at radii and metallicities that 
are typical for the MW GC system (GCS). We do observe varying mass-ratios of the
simulated GC candidates relative to the observed mass in the MW and M31 GC systems
for different bins of galactocentric radius-metallicity ($r_{\text{gal}}$-[Fe/H]).
This may imply that different values for the combined product of the bound cluster 
formation efficiency and the GC disruption rate are needed. Overall, the Auriga 
simulations produce GC candidates with higher metallicities than the MW and M31 
GCS and they are found at larger radii than observed. Bound cluster formation
efficiencies higher than ten percent are needed for the metal-poor GC candidates,
and those within the Solar radius should experience negligible destruction rates.
GC candidates in the outer halo, on the other hand, should either have low formation
efficiencies, or experience high mass loss for the Auriga simulations to produce a
GCS that is consistent with that of the MW or M31. Finally, the scatter in the 
metallicity as well as in the radial distribution between different Auriga runs 
is considerably smaller than the differences between that of the MW and M31 GCSs. 
The Auriga model is unlikely to give rise to a GCS that can be consistent with
both galaxies.
\end{abstract}

@@

The literature offers a wealth of formation scenarios. \citet{1968ApJ...154..891P}
and \citet{1984ApJ...277..470P} argue that GCs form as the earliest bound
structures in the Universe (i.e. prior to formation of the main galaxy), 
noting that the Jeans length and mass shortly after recombination is consistent
with typical GC masses and sizes. \citet{2005MNRAS.364..367D} and \citet{
2009ApJ...706L.192B} argue that (the blue subpopulations of) GCs form in radially
biased dark matter halos at high redshift. Other recent hypotheses of GC formation 
prior to collapse of the proto-galaxy include formation in colliding supershells 
\citep{2017Ap&SS.362..183R}, in supersonically induced gaseous objects
\citep{2019arXiv190408941C}, or in high-speed collisions of dark matter subhaloes
\citep{2019arXiv190508951M}. \citet{2017MNRAS.472.3120B} suggests
that (the blue subpopulation of) GCs could form in high density regions along
the cosmic filament before or during collapse.

@@

Yet another hypothesis is that star cluster formation is triggered by major 
gas-rich (spiral) galaxy mergers \citep{1987nngp.proc...18S, 1992ApJ...384...50A},
which is naturally expected within the framework of hierarchical assembly. One
testable prediction of this scenario is the formation of young clusters in
interacting and merging galaxies, which has been observed and are found to show 
remarkable similarities with GCs in the MW \citep[e.g.][]{
1995AJ....109..960W, 1996AJ....112..416H, 1999AJ....118..752Z, 1999AJ....118.1551W}.
Moreover, modelling efforts of this framework yield GC (sub)populations consistent 
with various observables \citep[e.g.][]{2010ApJ...718.1266M, 2018MNRAS.480.2343C}, 
and the recent numerical simulation of an isolated dwarf-dwarf merger executed at 
very high resolution (baryonic mass $m_b \sim$~4M\Sun; softening $\epsilon = 0.1$~pc) 
produces star clusters that could be GC progenitors \citep{
2019arXiv190509840L}.

@@

In this work we use state of the art simulations that produce realistic spiral 
galaxies (MW analogues) at redshift zero for which several global properties 
are consistent with the observations. The question thus naturally arises whether 
the star formation histories of the simulations give rise to a GCS similar to 
the MW and/or M31 GCSs. In particular, 
we use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, 
further described in Section~\ref{sec:auriga}. We investigate whether the star 
formation model implemented produces metallicity, 
radial, and metallicity-radial distributions that are consistent with the MW 
and/or M31 GCSs, and whether the model produces enough stellar mass with
the right properties to allow for formation efficiencies lower than unity and
the expected (dynamical) mass loss over the cluster lifetime (not modelled 
explicitly in this study).

@@

The galaxy formation model includes primordial and metal-line cooling with 
self-shielding corrections. Reionization is completed at redshift six by a
time-varying spatially uniform UV background \citep{2009ApJ...703.1416F, 
2013MNRAS.436.3031V}. The interstellar medium (ISM) is described by an equation of 
state for a two-phase medium in pressure equilibrium \citep{2003MNRAS.339..289S}: 
cold clouds embedded in a hot ambient medium, whose mass and energy densities
are described by processes important for star formation, such as the condensation 
of cold clouds and the photoevaporation of clouds. Stars form stocastically in 
thermally unstable gas with a density threshold of $n = 0.13 \, \text{cm}^{-3}$,
and consecutive stellar evolution is accounted for. The channel for energetic
stellar feedback is from non-local SNII, which is modelled with wind particles
(\citealt{2014MNRAS.437.1750M}; \citetalias{2017MNRAS.467..179G}). Galactic 
winds enrich the ISM
with metals from SNIa, SNII, and AGB stars \citep{2013MNRAS.436.3031V}. Supermassive
black holes grow via Bondi–Hoyle–Lyttleton accretion \citep{1944MNRAS.104..273B,
1952MNRAS.112..195B}, and feedback from the active galactic nuclei has a low-accretion
and high-accretion mode (radio and quasar) (\citealt{2005MNRAS.361..776S, 
2014MNRAS.437.1750M}; \citetalias{2017MNRAS.467..179G}). Finally, the simulations 
follow the evolution of a magnetic field of $10^{-14}$ (comoving)~G seeded at 
$z = 127$ \citep{2013MNRAS.432..176P, 2014ApJ...783L..20P}.

>>>>

% Abstract of the paper
\begin{abstract}
We investigate whether the galaxy and star formation model used for the Auriga
simulations can produce a realistic globular cluster (GC) population. 
We compare statistics of GC 
candidate star particles in the Auriga haloes with catalogues of the Milky Way 
(MW) and Andromeda (M31) GC populations. We find that the Auriga simulations do 
produce sufficient stellar mass for GC candidates at radii and metallicities that 
are typical for the MW GC system (GCS). We do observe varying mass-ratios of the
simulated GC candidates relative to the observed mass in the MW and M31 GC systems
for different bins of galactocentric radius-metallicity ($r_{\text{gal}}$-[Fe/H]).
This may imply that different values for the combined product of the bound cluster 
formation efficiency and the GC disruption rate are needed. Overall, the Auriga 
simulations produce GC candidates with higher metallicities than the MW and M31 
GCS and they are found at larger radii than observed. Bound cluster formation
efficiencies higher than ten percent are needed for the metal-poor GC candidates,
and those within the Solar radius should experience negligible destruction rates.
GC candidates in the outer halo, on the other hand, should either have low formation
efficiencies, or experience high mass loss for the Auriga simulations to produce a
GCS that is consistent with that of the MW or M31. Finally, the scatter in the 
metallicity as well as in the radial distribution between different Auriga runs 
is considerably smaller than the differences between that of the MW and M31 GCSs. 
The Auriga model is unlikely to give rise to a GCS that can be consistent with
both galaxies.
\end{abstract}

@@

The literature offers a wealth of formation scenarios. \citet{1968ApJ...154..891P}
and \citet{1984ApJ...277..470P} argue that GCs form as the earliest bound
structures in the Universe (i.e. prior to formation of the main galaxy), 
noting that the Jeans length and mass shortly after recombination is consistent
with typical GC masses and sizes. \citet{2005MNRAS.364..367D} and \citet{
2009ApJ...706L.192B} argue that (the blue subpopulations of) GCs form in radially
biased dark matter (DM) halos at high redshift. Other recent hypotheses of GC formation 
prior to collapse of the proto-galaxy include formation in colliding supershells 
\citep{2017Ap&SS.362..183R}, in supersonically induced gaseous objects
\citep{2019arXiv190408941C}, or in high-speed collisions of dark matter subhaloes
\citep{2019arXiv190508951M}. \citet{2017MNRAS.472.3120B} suggests
that (the blue subpopulation of) GCs could form in high density regions along
the cosmic filament before or during collapse.

@@

Yet another hypothesis is that star cluster formation is triggered by major 
gas-rich (spiral) galaxy mergers \citep{1987nngp.proc...18S, 1992ApJ...384...50A},
which is naturally expected within the framework of hierarchical assembly. One
testable prediction of this scenario is the formation of young clusters in
interacting and merging galaxies, which has been observed and are found to show 
remarkable similarities with GCs in the Milky Way (MW) \citep[e.g.][]{
1995AJ....109..960W, 1996AJ....112..416H, 1999AJ....118..752Z, 1999AJ....118.1551W}.
Moreover, modelling efforts of this framework yield GC (sub)populations consistent 
with various observables \citep[e.g.][]{2010ApJ...718.1266M, 2018MNRAS.480.2343C}, 
and the recent numerical simulation of an isolated dwarf-dwarf merger executed at 
very high resolution (baryonic mass $m_b \sim$~4M\Sun; softening $\epsilon = 0.1$~pc) 
produces star clusters that could be GC progenitors \citep{
2019arXiv190509840L}.

@@

In this work we use state of the art simulations that produce realistic spiral 
galaxies (MW analogues) at redshift zero for which several global properties 
are consistent with the observations. The question thus naturally arises whether 
the star formation histories of the simulations give rise to a GCS similar to 
the MW and/or Andromeda (M31) GCSs. In particular, 
we use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, 
further described in Section~\ref{sec:auriga}. We investigate whether the star 
formation model implemented produces metallicity, 
radial, and metallicity-radial distributions that are consistent with the MW 
and/or M31 GCSs, and whether the model produces enough stellar mass with
the right properties to allow for formation efficiencies lower than unity and
the expected (dynamical) mass loss over the cluster lifetime (not modelled 
explicitly in this study).

@@

The galaxy formation model includes primordial and metal-line cooling with 
self-shielding corrections. Reionization is completed at redshift six by a
time-varying spatially uniform UV background \citep{2009ApJ...703.1416F, 
2013MNRAS.436.3031V}. The interstellar medium (ISM) is described by an equation of 
state for a two-phase medium in pressure equilibrium \citep{2003MNRAS.339..289S}: 
cold clouds embedded in a hot ambient medium, whose mass and energy densities
are described by processes important for star formation, such as the condensation 
of cold clouds and the photoevaporation of clouds. Stars form stocastically in 
thermally unstable gas with a density threshold of $n = 0.13 \, \text{cm}^{-3}$,
and consecutive stellar evolution is accounted for. The channel for energetic
stellar feedback is from non-local type II supernovae (SN), which is modelled 
with wind particles (\citealt{2014MNRAS.437.1750M}; \citetalias{2017MNRAS.467..179G}).
Galactic winds enrich the ISM with metals from SNIa, SNII, and asymptotic giant 
branch (AGB) stars \citep{2013MNRAS.436.3031V}. Supermassive
black holes grow via Bondi–Hoyle–Lyttleton accretion \citep{1944MNRAS.104..273B,
1952MNRAS.112..195B}, and feedback from the active galactic nuclei has a low-accretion
and high-accretion mode (radio and quasar) (\citealt{2005MNRAS.361..776S, 
2014MNRAS.437.1750M}; \citetalias{2017MNRAS.467..179G}). Finally, the simulations 
follow the evolution of a magnetic field of $10^{-14}$ (comoving)~G seeded at 
$z = 127$ \citep{2013MNRAS.432..176P, 2014ApJ...783L..20P}.
